A quantitative framework for investigating the reliability of empirical network construction

### 2018-11-29 manuscript/reply_to_reviewers.tex

\begin{document}

\newpage

\setcounter{page}{1}

% Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly. Changed filtering to reflect all uncertainty, not just detection (more accurate, hopefully less confusing). No box needed, just "Why sample" section.

% Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli? Worthwhile to add a demo of Jensen's inequality?
% To do: expand discussion of our results as much as possible given space constraints.
% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

@@

	\begin{refquote}
	Your manuscript has been assessed by four different referees who agree that you touch upon a very important problem. However, they all feel your manuscript needs substantial improvements. They provide excellent advise on how to revise your manuscript and you should carefully consider all their comments. Overall, you do not acknowledge important past contributions and do not clearly explain the importance of the methodological issues you cover in your study. Importantly, referee 1 feels the real novelty of your study is the consideration of the importance and complexity of choosing prior information in constructing networks. Obviously, this is an issue in the context of Bayesian approaches, which are not necessarily well understood by empiricists, precisely the audience your manuscript should address. Please, follow very closely the suggestions of the referees when revising your manuscript.

	\end{refquote}

	\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address this. Reviewer 2's comments take a different view of the purpose and scope of the manuscript than the other reviewers; we respect their ideas but feel that some are beyond the scope of the present manuscript. In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework. We emphasize that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work). The novelty and impact of our work lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience. Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4. We hope that, in the course of these revisions, we have at least partially addressed Reviewer 2's concerns as well. 
	\smallskip
	We have taken Reviewer 1's suggestion that we expand upon the different types of priors available and reasons for choosing one over the other. We also now offer a brief discussion about concerns over the subjectivity of prior selection. We argue that a great deal of subjectivity is baked into the compilation of empirical networks and that a Bayesian approach can be seen as making this subjectivity explicit. We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of "forbidden links"). We hope that our revision more clearly frames the importance of uncertainty in ecological networks and positions a simple Bayesian approach as a partial solution (together with high-quality sampling, of course). 
	\smallskip
	We have also added many references to prior work. While the present study is not intended to be a full review of the literature, we certainly do not wish to downplay other workers in the area.
	\smallskip
	Finally, several of the Reviewers appeared to believe that we were advocating for reduced sampling effort. That is emphatically not the case (we find the idea absurd), and we have revised the manuscript to be clearer about the fact that increased sampling effort can reduce some sources of uncertainty. We hope that it is now clear that the Bayesian framework we promote is a complement to high sampling effort.

	Once again, we thank the Associate Editor and Reviewers for their comments and hope that our revised manuscript will satisfy their concerns.

@@

\newpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1} [[done]]
% ---------------------------------------

	1. Suggestion to refocus on prior selection [[done]]

@@

		\textbf{R:} We thank the Reviewer for the suggestion to expand our discussion of prior selection, particularly with regard to approxmimate/empirical Bayes. Although we are somewhat space-limited, we have expanded our description of different priors available and why a researcher might choose one over another (lines XX-XX). We also touch upon the controversy over using empirical priors (lines XX-XX) although we were unable to find many references addressing this in detail. If the Reviewer has particular works in mind, we would be more than happy to include them. We hope that this expanded description will be a better guide for empiricists who may not be familiar with Bayesian statistics.
		\medskip
		We also appreciate the Reviewer's comments on our introduction. We feel that understanding the problem of uncertain detection of interactions is important motivation for a reader not already familiar with Bayesian procedures to wade through a larger discussion on priors. Therefore we have revised and, hopefully, streamlined our discussion but do not jump straight in to priors. We have, however, taken care to introduce our analysis as a worked example (lines XX-XX) and hope that this helps to reduce the conflict between the introduction and our data. 
		\medskip
		We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach. We have refined the introduction to be more specific about the problem we are attempting to solve. We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.

@@

	2. Suggestion to add more literature [[done]]

		\begin{refquote}
		The introduction flows well and is thoughtfully laid out. Given the enormous amount of literature in the field, it is not possible to provide a full set of citations. However, it seems remiss to not consider Jordano (2016) in the sampling section.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the literature recommendations. We have incorporated these reference as suggested. Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript ('narrowing our net'). We hope that this revised introduction will also meet with the Reviewer's approval.

@@

	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes [[done]]

		\begin{refquote}
		It’s a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
		\end{refquote}

		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution we use. We now introduce the MLE formally within this context (lines XX-XX) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (lines XX-XX).

		Lines XX-XX:

		\begin{quotation}
			The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$. The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
		\end{quotation}

		Lines XX-XX:

		\begin{quotation}
			The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
		\end{quotation}

@@

		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion. We emphasize the board applicability of our approach across network types and systems with varying degrees of prior knowledge. We also emphasize that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders). We hope that the contribution our manuscript makes is now clearer.

	6. Potential contradiction [[done]]

		\begin{refquote}
		L89 for example, seems to conflict with the two paragraphs immediately following it?
		\end{refquote}

		\textbf{R:} We now address questions of sampling in the subsection \textbf{Why can't we sample more?}. We hope that this revision makes it clear that sampling should be as high-quality as possible but that sampling is unlikely to completely remove uncertainty.

@@

		\begin{refquote}
			Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
		\end{refquote}

		\textbf{R:} We have rephrased the end of this paragraph to mention previous predictive models dealing with uncertainty in interaction matrices.

		\begin{refquote}
		Line 89.  In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).  I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.
		\end{refquote}

		\textbf{R:} We have revised this section and now no longer refer to the specifics of Weinstein and Graham at all. Instead, we discuss repeated sampling in a section dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certinaly not). We hope that this is less confusing.

@@

		\begin{refquote}
		3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		\medskip
		Line 240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal…
		\medskip
		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
		\end{refquote}

		\textbf{R:} We have expanded our introduction of the case study (lines XX-XX) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions. This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in number of methodologies, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above. We repeat this point in the discussion to ensure that the case study is relevant. We have also clarified our statement that strict Bayes does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines XX-XX). As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.

		\begin{quotation}

 			To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details). 
      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together. Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda$).
      We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).

	4. Misunderstanding of our point about sampling effort [[done]]

		\textbf{R:} We believe that the Reviewer has badly misunderstood the point of our comments on sampling effort. Several of their comments suggest that we are advocating for reducing sampling effort. This is emphatically not the case. Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would not be helpful. We now address this assumption explicitly in a section dedicated to the potential for sampling effort to reduce uncertainty about interactions (\textbf{Why can't we sample more?}. Below, we address the Reviewer's sampling-related comments one by one.

@@

		\begin{refquote}
		Line 130.  The ideas here are largely a repeat from those above.  Further, while it may be true that we can sample too much – I think it is dangerous to suggest we should sample less – do the authors think that sampling across most network studies is sufficient (the opposite is stated in the discussion)?  I wonder if the argument is a bit more statistical than biological.
		\end{refquote}

		\textbf{R:} We agree that it is dangerous to suggest that anyone sample less, that is why we have not done so. We argue only that the amount of sampling required to be confident that co-occurring species do not interact is large -- likely beyond what is feasible for speciose systems given the limited resources available to many researchers. Sampling across most network studies is almost certainly not sufficient, but data which would allow readers to judge this (i.e., number of times each species is observed, independent of numbers of observed interactions) is not generally provided. We chose to be more charitable than the Reviewer and assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources. Infinite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.

		\begin{refquote}
		Line 144.  I am much more comfortable with this statement than how sampling effort should be considered and I would suggest moving this up and then explaining how even if we sample well we need to consider uncertainty for the reasons you mention in the previous section.  Please note that you make the same point in your discussion on line 338.
		\end{refquote}

		\textbf{R:} We are pleased that this point was clear and have made sure to include it in our revision.

@@

		\begin{refquote}
		Line 319.  It is clear that these are large samples but if interaction among co-occurring species was greater than you need lower samples – correct?  Should this be made clear?  Otherwise, we maybe can just never get enough data!
		\end{refquote}

		\textbf{R:} We are specifically speaking about interactions which were never observed. As interaction networks tend to be sparse, there will always be many of these. If interaction frequencies were higher among species that co-occurred, then we would have fewer unobserved interactions but the sample sizes needed to be confident that an unobserved interaction does not occur would not change (perhaps our threshold for deciding to believe a zero might, which is why we provide sample sizes for several thresholds). The Reviewer has hit the nail on the head with the idea that it is extremely hard to get enough data to be sure about every interaction. This is why prior knowledge can be so useful!

@@

		\begin{refquote}
		Line 338 to 342.  Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????
		\end{refquote}

		\textbf{R:} We had written our first draft with the assumption that empirical ecologists are well aware that large sample sizes are important and that they should sample as much as possible. Given that, repeating the call to sample more seemed more likely to come across as patronizing than helpful. We did not anticipate that anyone would read the omission of such a call a statement that anyone should sample \emph{less}. In our revised manuscript, we collect our discussion of sampling into a dedicated section. We hope that this will make it clearer that sampling is very important but cannot completely eliminate uncertainty (except perhaps in some very species-poor and unusually static systems, but these are certainly rare). As to adding more zeros than ones specifically, this is only "bad" in the sense that it gives us more high-uncertainty cells in the interaction matrix. We take the view that it is better to have "known unknowns" than "unknown unknowns" and it is certainly better to know about more of the species in a community than fewer, but finding a single individual of a rare species will not reduce uncertainty in the web. We have added a line (XX-XX) specifically to address this.

		\begin{quotation}
			we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
		\end{quotation}

@@

		\textbf{R:} As we did not intend to write a review, we understand the Reviewer's complaint. This shows that we did not clearly establish the purpose of our manuscript, and we hope that our revision corrects this. In particular, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it. Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this.

	1. Paper is poorly structured [[done?]]

		\begin{refquote}
		However, I felt that the structuring of the paper made it a challenge to understand and apply. It felt like the paper itself had been written in different sections (by different authors?) with not enough links between the sections. I also felt that there was a strong theoretical component, which is important, but there needed to be a stronger link with the issues around empirical ecology, as explained below.
		\end{refquote}

		\textbf{R:} We have revised the manuscript with an eye to clarifying the flow between sections. We hope that it is now clear that our proposed framework is designed to use Bayesian theory to complement empirical networks and empiricists' detailed knowledge of their systems.

@@

	3. Comment on weighted metrics [[done]]

		\begin{refquote}
		L36ff The authors should note the value of weighted metrics in taking account of sampling biases.
		\end{refquote}

		\textbf{R:} We do not see how weighted metrics (which we infer mean metrics including interaction strength/frequencies based on the Reviewer's comment below) account for sampling biases. It seems to us that measures of interaction strength should be \emph{more} susceptible to sampling biases, not less, as abundant species are both more likely to have their interactions recorded and more likely to have these interactions recorded as strong/frequent. We have rephrased the introduction so that the original line 36 no longer appears. If the Reviewer strongly feels that weighted metrics somehow do sampling biases, we must ask for clarification as to why. We are willing to add a note as requested, but only if we are convinced that weighted metrics are indeed useful in this regard.

	4. Demand for extension to weighted networks [[not done - do we want to do this?]]

@@

		\begin{quotation}
			To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems. Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in order to assemble a metaweb. We then demonstrate this approach using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a metaweb allows us to establish confidence intervals around measures of network structure.
			\end{quotation}

	9. Misunderstanding of how biased sampling does not solve problems of uncertainty [[done]]

		\begin{refquote}
		L136 This is a completely different issue, that you do not address in the paper.
		\end{refquote}

		\textbf{R:} We do not believe that biased sampling is a completely different issue as the tendency for some interactions to be sampled more easily than others clearly contributes to varying levels of detection uncertainty. Increasing sampling effort will not do much good if we repeatedly sample the same common interactions and very rarely identify any new interactions. We now address questions about whether or not sampling more will remove uncertainty in a dedicated section (\textbf{Why can't we just sample more?}). We still mention the fact that increased sampling will not reduce uncertainty evenly across interactions as this is an important point to consider when designing sampling protocols and when analysing empirical data. We also point out that combining sampling types is a partial solution to this problem; if different sampling methods have different biases, they may partially cancel each other out. We believe that this addresses the question as much as possible given our focus on analysing collected data rather than collecting new data.

### 2018-11-29 manuscript/reply_to_reviewers.tex

			\begin{quotation}
				Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
			\end{quotation}

		Note that our model is not concerned with partitioning different sources of variation; the filtering levels we present therefore represent uncertainty from all sources. As such, comparing them directly to "typical sampling effort" would be an apples-to-oranges comparison. We do note that~\citet{Weinstein2017a} found a detectability of 23.3\% for interactions despite high sampling effort,~\citet{Jordano2016} found that about half of unobserved interactions did not qualify as "forbidden links", and~\citet{Bartomeus2013} found that 59\% of interactions were detected. We therefore do not think that the range of filtering levels we applied were particularly unreasonable (although we note that none of the above studies refer to plant-galler networks). That said, the Reviewer is correct that the values we chose were absolutely arbitrary. To make this clear, we now filter in 10\% increments from 90\% to 10\% to illustrate a broader range of uncertainty.

	17. Expand discussion of results on line 321 [[not done - will take this after we see about space]]

### 2018-11-29 manuscript/CI_interactions.tex
reply ready for co-authors

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C), thereby adding more zeros with high uncertainty (which would require more sampling to reduce, and so on).

>>>>

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
